\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-06 manuscript/main.tex
modified:   analysis/final_analysis.do 	new file:   analysis/quantile-regression.R 	modified:   manuscript/main.tex

@@

\textbf{Finish Theoretical Model by May 20th, Finish the Online Appendix, Empirical Finding by May 25th, and Finish the Discussion and Conclusion by May 30th.}

@@

@@

\begin{assumption}[homogenous brokerage]
  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages. We have $\alpah_1 > \alpha_s$.
\end{assumption}

@@

>>>>

\textbf{Now I think about how to do this, the first task is to write completely the model and estimation of the offline and platform's effect with offline is the brokerage's offline store's entry and the onlien is the platofmrization strategy.}

@@

@@

From Table \ref{tab:statistical} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 higher than those neighborhoods without lianjia. Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.  This significance difference suggests that if we treat our sample as a cross sectional data and estimate the result with static model without considering the individual fixed effect, we may get a biased result. Besides, our model may suffer from endogeneity issue, since the number of lianjia's stores may be endogenous to the transaction price and the number of stores.

@@

@@

We can try to decompose the

% \begin{assumption}[homogenous brokerage]
%  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages. We have $\alpah_1 > \alpha_s$.
% \end{assumption}
